A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-30 paper/paper.tex
Type set the inversion lemma for set

@@

\begin{lemma}[ST-Set]
  If $[[|= G]]$ and $[[i < j]]$, then $[[G |= Set i : Set j]]$.
\end{lemma}

\begin{lemma}[ST-Pi]
  If $[[G |= A : Set i]]$ and $[[G ++ A |= B : Set i]]$, then $[[G |= Pi
  A B : Set i]]$.
\end{lemma}

>>>>

\begin{lemma}[Set Inv]
  \label{lemma:setinv}
  The following two statements are equivalent:
  \begin{itemize}
  \item $[[G |= A : Set i]]$
  \item For all $[[rho]]$, if $[[rho |= G]]$, then there exists
    $[[S]]$ such that $[[InterpR i (A {rho}) S]]$
  \end{itemize}
\end{lemma}
\begin{proof}
  The forward direction is immediate by
  Lemma~\ref{lemma:interpinv}. We now consider the backward direction
  and show that $[[G |= A : Set i]]$ given the second bullet.

  Suppose $[[rho |= G]]$, then we know that there exists some $[[S]]$
  such that $[[InterpR i (A {rho}) S]]$. By the definition of semantic
  typing, it suffices to show that there exists some $[[j]]$ and
  $[[S0]]$ such that  $[[InterpR j Set i S0]]$ and $[[A {rho} in
  S0]]$.
  Pick $[[S i]]$ for $[[j]]$ and $[[ { A | exists S , InterpR i A S }
  ]]$ for $[[S0]]$ and it's trivial to verify the conditions hold.
\end{proof}

@@

\begin{lemma}[ST-Set]
  If $[[i < j]]$, then $[[G |= Set i : Set j]]$.
\end{lemma}
\begin{proof}
  Immedaite by Lemma~\ref{lemma:setinv} and \rref{I-Set}.
\end{proof}

\begin{lemma}[ST-Pi]
  If $[[G |= A : Set i]]$ and $[[G ++ A |= B : Set i]]$, then $[[G |= Pi
  A B : Set i]]$.
\end{lemma}
\begin{proof}
  Suppose $[[rho |= G]]$. Applying
% Our goal is to show that there exists some
%   $[[S]]$ such that $[[InterpR i Pi A B S ]]$.
%   From the premise $[[G |= A : Set i]]$, we know that there exists
%   some $[[S0]]$ such that
\end{proof}
